---
title: "FinalProject"
author: "Joshua Sum"
date: "2/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Potential Business Questions

These are the business questions that we were thinking of answering when we initially found our dataset:

- What is the ideal Shark Tank pitch that gives a competitor the best shot of getting funded at the highest valuation?
- Which target should you try to tailor your pitch to, depending on what your company does?

# Shark Tank Data
We obtained our data from a Kaggle project https://www.kaggle.com/zabonpan/shark-tank-pitches-deals-season-111

We started with needing clean the data, because there were some rows with incomplete data values.

```{r}
data <- read.csv("SharkTankData.csv")

# Taking subset of season 5 onwards
data <- subset(data, Season >= 5)
data$ASK_Equity <- as.numeric(substr(data$ASK_Equity,1,nchar(data$ASK_Equity)-1))/100
data$ASK_Amount <- as.numeric(gsub(",", "", data$ASK_Amount))
data$ASK_Valuation <- as.numeric(gsub(",", "", data$ASK_Valuation))
data$ASK_Equity <- ifelse(is.na(data$ASK_Equity), 0, data$ASK_Equity)
data$ASK_Amount <- ifelse(is.na(data$ASK_Amount), 0, data$ASK_Amount)
data$ASK_Valuation <- ifelse(is.na(data$ASK_Valuation), 0, data$ASK_Valuation)

data$DEAL_Equity <- as.numeric(substr(data$DEAL_Equity,1,nchar(data$DEAL_Equity)-1))/100
data$DEAL_Amount <- as.numeric(gsub(",", "", data$DEAL_Amount))
data$DEAL_Valuation <- as.numeric(gsub(",", "", data$DEAL_Valuation))
data$DEAL_Equity <- ifelse(is.na(data$DEAL_Equity), 0, data$DEAL_Equity)
data$DEAL_Amount <- ifelse(is.na(data$DEAL_Amount), 0, data$DEAL_Amount)
data$DEAL_Valuation <- ifelse(is.na(data$DEAL_Valuation), 0, data$DEAL_Valuation)

data$Investment.shark <- as.numeric(gsub(",", "", data$Investment.shark))
data$Investment.shark <- ifelse(is.na(data$Investment.shark), 0, data$Investment.shark)
data$X..Sharks <- ifelse(is.na(data$X..Sharks), 0, data$X..Sharks)
data$Loan <- ifelse(data$Loan == "Y", 1, data$Loan)
data$Loan <- ifelse(data$Loan == "N", 0, data$Loan)
data$Loan <- ifelse(is.na(data$Loan), 0, as.numeric(data$Loan))
data$State <- NULL
data$Business <- NULL
data$Description <- NULL
data$Notes <- NULL
data$Category <- as.factor(data$Category)
data$Entrepreneur.Gender <- as.factor(data$Entrepreneur.Gender)
data$Royalty <- as.factor(data$Royalty)
data$Barbara.Corcoran <- as.factor(data$Barbara.Corcoran)
data$Mark.Cuban <- as.factor(data$Mark.Cuban)
data$Lori.Greiner <- as.factor(data$Lori.Greiner)
data$Robert.Herjavec <- as.factor(data$Robert.Herjavec)
data$Daymond.John <- as.factor(data$Daymond.John)
data$Kevin.O.Leary <- as.factor(data$Kevin.O.Leary)
data$Guest <- as.factor(data$Guest)

summary(data)
```

## Getting Data Ready for Analysis

Next we get our dataset ready for analysis.

```{r}
library(lmtest)
library(aod)
library(caret)
library(VGAM)
library(class)
library(gmodels)
library(C50)

# Randomize the rows in the data (shuffling the rows)
set.seed(12345)
shark_rand <- data[sample(1:nrow(data)),]

# Selects 10000 random rows for test data
test_set <- sample(nrow(shark_rand), 50)
# Depending on R-version and computer, different rows may be selected. 
# If that happens, results are different. 

# Create a train set and test set
#First the predictors - all columns except the Deal column
shark_train <- shark_rand[-test_set,  -match("Deal",names(shark_rand))]
shark_test <- shark_rand[test_set,  -match("Deal",names(shark_rand))]

#Now the response (aka Labels) - only the Deal column
shark_train_labels <- shark_rand[-test_set, "Deal"]
shark_test_labels <- shark_rand[test_set, "Deal"]
shark_labels <-shark_rand[,"Deal"]
```

## Creating a Logistic Regression Model



```{r}
linear_model = glm(shark_train_labels ~ ., data = shark_train, family ="binomial")
summary(linear_model)
results <- shark_test
results$pred_glm <- predict(linear_model, newdata = shark_test, type = "response")
results$pred_glm <- as.factor(ifelse(results$pred_glm > 0.5, 1, 0))
confusionMatrix(results$pred_glm, as.factor(shark_test_labels), positive = "1")
```



## Creating a KNN Model

```{r}
#Normalize the data
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# we are going to normalize everything 
shark_mm <- as.data.frame(model.matrix(~.-1,shark_rand))
shark_norm <- as.data.frame(lapply(shark_mm, normalize))

norm_sample <- sample(nrow(shark_norm), 128)

# Create a train set and test set
#First the predictors - all columns except the Deal column
norm_train <- shark_norm[-norm_sample, -match("Deal",names(shark_norm)) ]
norm_test <- shark_norm[norm_sample, -match("Deal",names(shark_norm)) ]

#Now the response (aka Labels) - only the Deal column
norm_train_labels <- shark_norm[-norm_sample, "Deal"]
norm_test_labels <- shark_norm[norm_sample, "Deal"]



predict_knn <- knn(train = norm_train, test = norm_test,
                      cl = as.factor(norm_train_labels), k=21)

summary(predict_knn)
predict_knn <- as.factor(predict_knn)

CrossTable(x = predict_knn, y = norm_test_labels, prop.chisq = FALSE)
confusionMatrix(as.factor(norm_test_labels), predict_knn, positive = "1")
```

## Creating a Decision Tree to Predict if a business can get a Deal

After working on kNN we tried making a decision tree model to see if it would become more accurate. It turns out that a decision tree would be more accurate than a kNN model.

One major thing we noticed, however, was that there were specific columns that include the results, so those columns needed to be removed from the training data. For example, the column labeled DEAL_Equity must be removed because a row would only have this data when a deal actually occured.

```{r}

# Remove data that only Deals would have
removed_data <- shark_rand

removed_data$Deal <- as.factor(removed_data$Deal)
removed_data$DEAL_Equity <- NULL
removed_data$DEAL_Amount <- NULL
removed_data$DEAL_Valuation <- NULL
removed_data$Royalty <- NULL
removed_data$Loan <- NULL

removed_data$Barbara.Corcoran <- NULL
removed_data$Mark.Cuban <- NULL
removed_data$Lori.Greiner <- NULL
removed_data$Robert.Herjavec <- NULL
removed_data$Daymond.John <- NULL
removed_data$Kevin.O.Leary <- NULL
removed_data$Guest <- NULL
removed_data$Num.of.Sharks <- NULL
removed_data$Investment.shark <- NULL
removed_data$X..Sharks <- NULL

mod1 <- C5.0(Deal ~ ., data = removed_data)

predicted_shark <- predict(mod1, removed_data)
shark_labels <- as.factor(shark_labels)

CrossTable(x = shark_labels, y = predicted_shark, prop.chisq = FALSE)
confusionMatrix(predicted_shark, shark_labels, positive = "1")
```

